Red States = Red Flags?

### 2024-02-15 paper/paper.qmd

library(tidyverse)

@@

why is it important the structure of the paper

@@

Model Information Dependent variable: birth rate per 1000 population
Independent variables:State min wage, Abortion delay, Child enforcement
expenditure, Political affiliation

@@

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```
We run the model in R [@citeR] using the rstanarm package of @rstanarm.
We use the default priors from rstanarm.

@@

Our results are summarized in @tbl-modelresults.

```{r echo=FALSE, message=FALSE}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))

@@

{r} #\| echo: false #\| eval: true #\| label: tbl-modelresults #\|
tbl-cap: "Explanatory models of flight time based on wing width and wing
length" #\| warning: false

modelsummary::modelsummary( list( "First model" = first_model ),
statistic = "mad", fmt = 2 )

@@

```{r echo=FALSE, message=FALSE}
library(haven)
library(tidyverse)
library(tidyr)

@@

```{r echo=FALSE, message=FALSE, results='asis'}
library(knitr)
library(readxl)
library(dplyr)
library(ggplot2)

@@

<!-- -->

@@

```{r echo=FALSE, message=FALSE}
library(readxl)
library(dplyr)
library(readr)

@@

```{r echo=FALSE, message=FALSE}
library(readxl)
library(dplyr)
library(readr)

@@

@@

{r} \# POLITICAL AFFILIATION MAP

@@

{r} #Education graph

@@

Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive
check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the
prior. This shows...

{r} #\| eval: true #\| echo: false #\| message: false #\| warning: false
#\| label: fig-ppcheckandposteriorvsprior #\| layout-ncol: 2 #\|
fig-cap: "Examining how the model fits, and is affected by, the data"
#\| fig-subcap: \["Posterior prediction check", "Comparing the posterior
with the prior"\]

pp_check(first_model) + theme_classic() + theme(legend.position =
"bottom")

posterior_vs_prior(first_model) + theme_minimal() +
scale_color_brewer(palette = "Set1") + theme(legend.position =
"bottom") + coord_flip()

Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

{r} #\| echo: false #\| eval: true #\| message: false #\| warning: false
#\| label: fig-stanareyouokay #\| fig-cap: "Checking the convergence of
the MCMC algorithm" #\| fig-subcap: \["Trace plot", "Rhat plot"\] #\|
layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")

References

>>>>

# Workspace Set up
library(tidyverse)
library(haven)
library(tidyr)
library(readxl)
library(dplyr)
library(readr)
library(knitr)
library(ggplot2)
```

@@

@@

Model InformationDependent variable: birth rate per 1000 populationIndependent variables:State min wage Abortion delay Child enforcement expenditure Political affiliation

@@

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```

We run the model in R [@citeR] using the rstanarm package of @rstanarm. We use the default priors from rstanarm.

@@

@@

@@

```{r echo=FALSE, message=FALSE}

@@

```{r echo=FALSE, message=FALSE, results='asis'}

@@

@@

```{r echo=FALSE, message=FALSE}

@@

```{r echo=FALSE, message=FALSE}
# Determine which states had a delay or no delay policy 
abortion_policy <- read_dta("../data/analysis_data/annual_policy/policyvars01_19.dta") %>%
  filter(year >= 2001, year <= 2019) %>%
  select(delay, stname, year)

@@

{r}
#INTREST DISTRO OVER TIME GRAPHS

The District of Columbia (DC) exhibits the largest increase, with its minimum wage rising by $7.85, from $6.15 in 2001 to $14.00 in 2019. Arizona (AZ) and Colorado (CO) also show substantial increases of $6.85 each.

Georgia (GA) and Wyoming (WY) stand out as the only states with no change in minimum wage, maintaining a rate of $5.15 across the years. It is worth noting that this rate is equal to the federal minimum wage between 1997 - 2007, suggesting that these states have not adjusted their minimum wage above the federal floor set at that time.

{r}
# MINIMUM WAGE GRAPH

The trend lines across the graphs indicate a general decline in birth rates. The decline is more pronounced in states that have implemented delay policies, suggesting a possible correlation between policy enactment and a faster reduction in birth rates. 
>>>>>>> 9e43bbea0ebd995129f3e0d14bc9e8ec625b3856

@@

```{r}
# POLITICAL AFFILIATION MAP
```

## First discussion point: Abortion 
```{r}

#relative average # of births in states delay

#relative average # of births in states w/o delay

#Second discussion: Political affiliation

```{r}
# POLITICAL AFFILIATION MAP
```

@@

```{r}
#Education graph
```

@@

```{r}
